---
execute: 
  echo: true
  warning: false
  
format: html
---

# Data processing and packages
```{r}
pacman::p_load(summarytools,
               skimr,
               psych,
               rempsyc,
               knitr,
               kableExtra,
               gtsummary,
               sjPlot)

source("scripts/01_preparation.R")

options(digits = 2)
```

# Labelling data

```{r}

var_label(study1$exposure) <- "Perceived Misinformation Exposure"
var_label(study1$sharing) <- "Perceived Misinformation Sharing"
var_label(study1$alg_aware) <- "Algorithmic Awareness"
var_label(study1$wsp) <- "Weekly Whatsapp use"
var_label(study1$ig) <- "Weekly Instagram use"
var_label(study1$fb) <- "Weekly Facebook use"
var_label(study1$yt) <- "Weekly Youtube use"
var_label(study1$tw) <- "Weekly Twitter use"
var_label(study1$tiktok) <- "Weekly Tiktok use"
var_label(study1$age) <- "Age"
var_label(study1$gender) <- "Gender"
var_label(study1$rm) <- "Metropolitan region"
var_label(study1$educ_level) <- "Educational level"


var_label(study2$exposure) <- "Perceived Misinformation Exposure"
var_label(study2$sharing) <- "Perceived Misinformation Sharing"
var_label(study2$obj_know) <- "Objective news knowledge"
var_label(study2$subj_know) <- "Subjective news knowledge"
var_label(study2$subj_know_def) <- "Knowledge overconfidence"
var_label(study2$alg_aware) <- "Algorithmic Awareness"
var_label(study2$counteract_algorithm) <- "Algorithmic actions/counteractions"
var_label(study2$wsp) <- "Weekly Whatsapp use"
var_label(study2$ig) <- "Weekly Instagram use"
var_label(study2$fb) <- "Weekly Facebook use"
var_label(study2$yt) <- "Weekly Youtube use"
var_label(study2$tw) <- "Weekly Twitter use"
var_label(study2$tiktok) <- "Weekly Tiktok use"
var_label(study2$age) <- "Age"
var_label(study2$gender) <- "Gender"
var_label(study2$rm) <- "Metropolitan region"
var_label(study2$educ_level) <- "Educational level"

study1 <- study1|>
  mutate(educ_level = set_value_labels(educ_level, c(
    "Primary education or less" = 1,
    "Incomplete secondary education" = 2,
    "Complete secondary education" = 3,
    "Post-secondary education" = 4,
    "College education or more" = 5
    )
  )
)

study2 <- study2|>
  mutate(educ_level = set_value_labels(educ_level, c(
    "Primary education or less" = 1,
    "Incomplete secondary education" = 2,
    "Complete secondary education" = 3,
    "Post-secondary education" = 4,
    "College education or more" = 5
    )
  )
)
```

# Data preparation

```{r}
study1 <- study1 %>%
  mutate(
    sharing_original = ifelse(is.na(sharing_original), NA, sharing_original)
    )

study2 <- study2 %>%
  mutate(
    sharing_original = ifelse(is.na(sharing_original), NA, sharing_original)
    )%>%
  filter(alg_lit == 1)

study1_model <- study1|>
  mutate_at(.vars = vars(gender, rm, sharing_categorical),
            .funs = list(~to_label(.)))|>
  mutate_at(.vars = vars(ppal_ocupation,educ_level),
            .funs = list(~to_numeric(.)))

study2_model <- study2|>
  mutate_at(.vars = vars(gender,rm,sharing_categorical),
            .funs = list(~to_label(.)))|>
  mutate_at(.vars = vars(ppal_ocupation,educ_level),
            .funs = list(~to_numeric(.)))
```

# Table 1. Predicting Misinformation Exposure and Sharing in Study 1

```{r}
exposure_a <- lm(
  exposure ~
    alg_aware +
    age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study1_model
)

sharing_a_original <- lm(
  sharing_original ~ 
    alg_aware +
    age +  gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study1_model
)

sjPlot::tab_model(
  list(exposure_a, sharing_a_original),
  show.ci = FALSE,
  dv.labels = c("Exposure", "Sharing"),
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  string.pred = "Predictors",
  string.est = "β",
  show.se = T,
  transform = NULL,
  title = "Table 1. Predicting Missinformation Exposure and Sharing in Study 1"
)
```

# Table 2. OLS Models for Study 2
```{r}
exposure_3b <- lm(exposure ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                data=study2_model)

obj_know_model<-lm(obj_know ~ alg_aware+counteract_algorithm+
                     age+gender+rm+educ_level+
                     wsp+ig+fb+yt+tw+tiktok,
                   data=study2_model)

subj_know_model <- lm(subj_know ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                      wsp+ig+fb+yt+tw+tiktok,
                  data=study2_model)

score_model <- lm(subj_know_def ~ alg_aware+counteract_algorithm+
                        age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                      data=study2_model)

sjPlot::tab_model(exposure_3b,obj_know_model,subj_know_model,score_model,
          show.ci = FALSE,
          dv.labels = c("Perceived Misinformation Exposure",
                        "Objective news knowledge",
                        "Subjective news knowledge",
                        "Knowledge overconfidence"),
          pred.labels = c("(Intercept)",
                          "Alg. Awareness",
                          "Alg. counteractions",
                          "Age",
                          "Gender (Women = 1)",
                          "Metropolitan Region", 
                          "Educational level",
                          "Whatsapp weekly use", 
                          "Instagram weekly use", 
                          "Facebook weekly use", 
                          "Youtube weekly use", 
                          "Twitter weekly use", 
                          "TikTok weekly use"),
          show.se = T,
          string.est = "β",
          title = "OLS models Study 2")
```

# Table 3. Multinomial model for Sharing Misinformation in Study 2

```{r}
library(nnet)

# Study 2: Multinomial model
sharing_b_original <- multinom(
  sharing_categorical ~
    alg_aware + counteract_algorithm +
    age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2_model,
  trace = FALSE
)

sjPlot::tab_model(
  list(
    sharing_b_original
  ),
  show.ci = FALSE,
  show.se = TRUE,
  dv.labels = c(
    "Sharing Study 2 Categorical (Multinomial)"
  ),
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Alg. counteractions",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  string.est = "b (logit)",
  transform = NULL,
  title = "Sharing study 2"
)
```

# Table A1. Descriptive Statistics of Study 1 Variables.

```{r}
library(dplyr)
library(knitr)
library(tibble)
library(sjlabelled)

# Variables A1: TODAS continuas (incluye sharing)
vars_cont_a1 <- c(
  "exposure",
  "sharing_original",
  "alg_aware",
  "wsp",
  "ig",
  "fb",
  "yt",
  "tw",
  "tiktok",
  "age",
  "gender",
  "rm",
  "educ_level"
)

labels_cont_a1 <- c(
  "Perceived misinformation exposure",
  "Perceived misinformation sharing (continuous)",
  "Algorithmic awareness",
  "Weekly Whatsapp use",
  "Weekly Instagram use",
  "Weekly Facebook use",
  "Weekly Youtube use",
  "Weekly Twitter use",
  "Weekly Tiktok use",
  "Age (continuous)",
  "Gender",
  "Metropolitan region",
  "Educational level"
)

# Convertir haven_labelled/factor a numérico para resumir como continuo
study1_num <- study1 |>
  mutate(across(all_of(vars_cont_a1), ~ to_numeric(.x)))

table_a1 <- tibble(var = vars_cont_a1, variable = labels_cont_a1) |>
  rowwise() |>
  mutate(
    descr = paste0(
      round(mean(study1_num[[var]], na.rm = TRUE), 2),
      " (",
      round(sd(study1_num[[var]], na.rm = TRUE), 2),
      ")"
    ),
    min = round(min(study1_num[[var]], na.rm = TRUE), 2),
    max = round(max(study1_num[[var]], na.rm = TRUE), 2),
    cronbach = "",
    missing = paste0(round(mean(is.na(study1_num[[var]])) * 100, 2), "%")
  ) |>
  ungroup() |>
  select(variable, descr, min, max, cronbach, missing)

table_a1 |>
  kable(
    col.names = c(
      "Variable",
      "Mean (SD)",
      "Min.",
      "Max.",
      "Cronbach's Alpha",
      "Missings (%)"
    )
  )
```

# Table A2. Rural and Urban Algorithmic Literacy differences in Study 1.

```{r}
library(dplyr)
library(tidyr)
library(janitor)

# =========================
# 1. Preparar variable zona
# =========================
study1_demo <- study1 %>%
  mutate(
    zona = case_when(
      tipo_zona == 1 ~ "Urban",
      tipo_zona == 2 ~ "Rural",
      TRUE ~ NA_character_
    )
  )%>%
  filter(!is.na(zona))

# =========================
# 2. Tamaño muestral
# =========================
n_zona <- study1_demo %>%
  count(zona, name = "N")

# =========================
# 3. Edad (media y sd)
# =========================
edad_zona <- study1_demo %>%
  group_by(zona) %>%
  summarise(
    mean_sd_age = paste0(mean(age, na.rm = TRUE)%>%round(0)," (", sd(age, na.rm = TRUE)%>%round(0), ")"),
    .groups = "drop"
  )

# =========================
# 4. Nivel educacional
# =========================
educ_zona <- study1_demo %>%
  count(zona, educ_level) %>%
  group_by(zona) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  ungroup()

# =========================
# 5. Algorithmic literacy
# =========================
alg_lit_zona <- study1_demo %>%
  group_by(zona) %>%
  summarise(
    alg_lit = paste0(sum(alg_lit == 1, na.rm = TRUE)," (",round(100 * mean(alg_lit, na.rm = TRUE), 1), ")"),
    .groups = "drop"
  )

# =========================
# 6. Diferencia de medias
# =========================
alg_aware_diff <- with(
  study1_demo,
  t.test(alg_aware ~ zona)
)

diff_table <- tibble(
  diff_means = alg_aware_diff$estimate[1] - alg_aware_diff$estimate[2],
  p_value    = alg_aware_diff$p.value
)

alg_aware_table <- data.frame(
  zona = c("Rural", "Urban"),
  alg_aware_mean = c("2.2 (p > 0.01)", "2.8")
)

# =========================
# 7. Gender by zone
# =========================
gender_zona <- study1_demo %>%
  mutate(
    gender_lab = case_when(
      gender == 1 ~ "Women",
      gender == 0 ~ "Men",
      TRUE ~ NA_character_
    )
  ) %>%
  count(zona, gender_lab) %>%
  group_by(zona) %>%
  mutate(
    gender_pct = round(100 * n / sum(n), 1),
    gender_freq_pct = paste0(n, " (", gender_pct, "%)")
  ) %>%
  ungroup() %>%
  select(zona, gender_lab, gender_freq_pct) %>%
  pivot_wider(
    names_from = gender_lab,
    values_from = gender_freq_pct
  )

gender_tabla <- data.frame(
  zona = c("Rural", "Urban"),
  gender = c("M: 184 (41%) / W: 265 (59%)", "M: 327 (43.5%) / W: 424 (56.5%)")
)

# =========================
# 8. Educational level by zone
# =========================
educ_zona <- study1_demo %>%
  mutate(
    educ_lab = case_when(
      educ_level == 1 ~ "Basic education",
      educ_level == 2 ~ "Middle school (incomplete)",
      educ_level == 3 ~ "Middle school (complete)",
      educ_level == 4 ~ "Technical higher education",
      educ_level == 5 ~ "University / Postgraduate",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(educ_lab)) %>%
  count(zona, educ_lab) %>%
  group_by(zona) %>%
  mutate(
    educ_pct = round(100 * n / sum(n), 1),
    educ_item = paste0(educ_lab, ": ", n, " (", educ_pct, "%)")
  ) %>%
  summarise(
    Education = paste(educ_item, collapse = "; "),
    .groups = "drop"
  )



# =========================
# 9. Tabla resumen principal
# =========================
tabla_principal <- n_zona %>%
  left_join(alg_lit_zona, by = "zona") %>%
  left_join(alg_aware_table, by = "zona") %>%  
  left_join(edad_zona, by = "zona") %>%
  left_join(gender_tabla, by = "zona") %>%
  left_join(educ_zona, by = "zona") %>%
  rename(
    "Area" = zona,
    "Know Algorithmic Term" = alg_lit,
    "Algorithmic Awareness mean" = alg_aware_mean,
    "Age Mean (sd)" = mean_sd_age,
    "Gender" = gender
  )


tabla_principal %>%
  kable()
#openxlsx::write.xlsx(tabla_principal, "data/rural_comparation_study1.xlsx")

  
```

# Table A3. Summary Study 2 Variables.
```{r}
library(dplyr)
library(knitr)
library(tibble)

# Variables continuas para A3 (todas salvo sharing)
vars_cont <- c(
  "exposure",
  "obj_know",
  "subj_know",
  "subj_know_def",
  "alg_aware",
  "counteract_algorithm",
  "wsp", "ig", "fb", "yt", "tw", "tiktok",
  "age", "gender", "rm", "educ_level"
)

labels_cont <- c(
  "Perceived misinformation exposure",
  "Objective news knowledge",
  "Subjective news knowledge",
  "Overconfidence knowledge",
  "Algorithmic Awareness",
  "Algorithmic actions/counteractions",
  "Weekly Whatsapp use",
  "Weekly Instagram use",
  "Weekly Facebook use",
  "Weekly Youtube use",
  "Weekly Twitter use",
  "Weekly Tiktok use",
  "Age (continuous)",
  "Gender",
  "Metropolitan region",
  "Educational level"
)

a3_cont <- tibble(var = vars_cont, variable = labels_cont) |>
  rowwise() |>
  mutate(
    descr = paste0(
      round(mean(study2[[var]], na.rm = TRUE), 2),
      " (", round(sd(study2[[var]], na.rm = TRUE), 2), ")"
    ),
    min = round(min(study2[[var]], na.rm = TRUE), 2),
    max = round(max(study2[[var]], na.rm = TRUE), 2),
    cronbach = "",
    missing = paste0(round(mean(is.na(study2[[var]])) * 100, 2), "%")
  ) |>
  ungroup() |>
  select(variable, descr, min, max, cronbach, missing)

# sharing_categorical: frecuencias por categoría
sharing_freq <- study2 |>
  filter(!is.na(sharing_categorical)) |>
  count(sharing_categorical, name = "n") |>
  mutate(
    pct = round(100 * n / sum(n), 1),
    item = paste0(sharing_categorical, ": ", n, " (", pct, "%)")
  ) |>
  summarise(txt = paste(item, collapse = "; ")) |>
  pull(txt)

sharing_row <- tibble(
  variable = "Perceived misinformation sharing (categorical)",
  descr = sharing_freq,
  min = NA_real_,
  max = NA_real_,
  cronbach = "",
  missing = paste0(round(mean(is.na(study2$sharing_categorical)) * 100, 2), "%")
)

# Insertar sharing como segunda fila
table_a3 <- bind_rows(
  a3_cont |> slice(1),
  sharing_row,
  a3_cont |> slice(2:n())
)

table_a3 |>
  kable(
    col.names = c("Variable", "Mean (SD)/Prop.", "Min.", "Max.", "Cronbach's Alpha", "Missings (%)")
  )
```

# Table A4. Comparative models study 1 (Filter Alg. Lit.)

```{r}
s1_filter1 <- study1|>
  filter(alg_lit_test == 1)|>
  mutate(
    gender = to_label(gender),
    rm = to_label(rm)
  )

s1_filter2 <- study1|>
  filter(alg_lit_test == 0)|>
  mutate(
    gender = to_label(gender),
    rm = to_label(rm)
  )

exposure_a <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study1_model)

exposure_filter_a <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = s1_filter1)

exposure_interaction_a <- lm(exposure ~ 
                   alg_aware*alg_lit_test + 
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study1_model)

sharing_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")

sharing_filter_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                
                   data = s1_filter1,family = "binomial")

sharing_interaction_a <- glm(sharing~
                   alg_aware*alg_lit_test + 
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")

# lm.beta(exposure_a)
#lm.beta(exposure_filter_a)

#effectsize::standardize_parameters(sharing_a)
#effectsize::standardize_parameters(sharing_filter_a)


sjPlot::tab_model(list(exposure_a, exposure_filter_a,
                       sharing_a, sharing_filter_a), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Exposure: Original","Exposure: Alg == 1",
                                "Sharing: Original", "Sharing: Alg == 1"),
                  string.est = c("β (OLS/Logit)"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Region (MR = 1)", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  title = "Table X. Comparative models study 1 (Filter Alg. Lit.)",
                  transform = NULL)
```