---
execute: 
  echo: false
  warning: false
  
format: html
---

```{r}

pacman::p_load(summarytools,
               skimr,
               psych,
               rempsyc,
               knitr,
               kableExtra,
               gtsummary,
               sjPlot)

source("scripts/01_preparation.R")

options(digits = 2)

```

```{r}

var_label(study1$exposure) <- "Perceived Misinformation Exposure"
var_label(study1$sharing) <- "Perceived Misinformation Sharing"
var_label(study1$alg_aware) <- "Algorithmic Awareness"
var_label(study1$wsp) <- "Weekly Whatsapp use"
var_label(study1$ig) <- "Weekly Instagram use"
var_label(study1$fb) <- "Weekly Facebook use"
var_label(study1$yt) <- "Weekly Youtube use"
var_label(study1$tw) <- "Weekly Twitter use"
var_label(study1$tiktok) <- "Weekly Tiktok use"
var_label(study1$age) <- "Age"
var_label(study1$gender) <- "Gender"
var_label(study1$rm) <- "Metropolitan region"
var_label(study1$educ_level) <- "Educational level"


var_label(study2$exposure) <- "Perceived Misinformation Exposure"
var_label(study2$sharing) <- "Perceived Misinformation Sharing"
var_label(study2$obj_know) <- "Objective news knowledge"
var_label(study2$subj_know) <- "Subjective news knowledge"
var_label(study2$subj_know_def) <- "Knowledge overconfidence"
var_label(study2$alg_aware) <- "Algorithmic Awareness"
var_label(study2$counteract_algorithm) <- "Algorithmic actions/counteractions"
var_label(study2$wsp) <- "Weekly Whatsapp use"
var_label(study2$ig) <- "Weekly Instagram use"
var_label(study2$fb) <- "Weekly Facebook use"
var_label(study2$yt) <- "Weekly Youtube use"
var_label(study2$tw) <- "Weekly Twitter use"
var_label(study2$tiktok) <- "Weekly Tiktok use"
var_label(study2$age) <- "Age"
var_label(study2$gender) <- "Gender"
var_label(study2$rm) <- "Metropolitan region"
var_label(study2$educ_level) <- "Educational level"

study1 <- study1|>
  mutate(educ_level = set_value_labels(educ_level, c(
    "Primary education or less" = 1,
    "Incomplete secondary education" = 2,
    "Complete secondary education" = 3,
    "Post-secondary education" = 4,
    "College education or more" = 5
    )
  )
)

study2 <- study2|>
  mutate(educ_level = set_value_labels(educ_level, c(
    "Primary education or less" = 1,
    "Incomplete secondary education" = 2,
    "Complete secondary education" = 3,
    "Post-secondary education" = 4,
    "College education or more" = 5
    )
  )
)
```

# Table A1. Descriptive Statistics of Study 1 Variables.

```{r}
library(knitr)

data.frame(
  variable = c(
    "Perceived misinformation exposure",
    "Perceived misinformation sharing",
    "Algorithmic Awareness",
    "Weekly Whatsapp use",
    "Weekly Instagram use",
    "Weekly Facebook use",
    "Weekly Youtube use",
    "Weekly Twitter use",
    "Weekly Tiktok use",
    "Age (continuous)",
    "Gender",
    "Metropolitan region",
    "Educational level"
  ),
  
  descr = c(
    paste0(round(mean(study1$exposure, na.rm = TRUE), 2), " (", round(sd(study1$exposure, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study1$sharing, na.rm = TRUE), 2), " (", round(sd(study1$sharing, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study1$alg_aware, na.rm = TRUE), 2), " (", round(sd(study1$alg_aware, na.rm = TRUE), 2), ")"),
    paste("1:", sum(study1$wsp == 1), "0:", sum(study1$wsp == 0)),
    paste("1:", sum(study1$ig == 1), "0:", sum(study1$ig == 0)),
    paste("1:", sum(study1$fb == 1), "0:", sum(study1$fb == 0)),
    paste("1:", sum(study1$yt == 1), "0:", sum(study1$yt == 0)),
    paste("1:", sum(study1$tw == 1), "0:", sum(study1$tw == 0)),
    paste("1:", sum(study1$tiktok == 1), "0:", sum(study1$tiktok == 0)),
    paste0(round(mean(study1$age, na.rm = TRUE), 2), " (", round(sd(study1$age, na.rm = TRUE), 2), ")"),
    paste("Female:", sum(study1$gender == 0), "Male:", sum(study1$gender == 1)),
    paste("Rm:", sum(study1$rm == 1), "Other:", sum(study1$rm == 0)),
    paste("Primary education or less:", sum(study1$educ_level == 1, na.rm = TRUE),
          "Incomplete secondary education:", sum(study1$educ_level == 2, na.rm = TRUE),
          "Complete secondary education:", sum(study1$educ_level == 3, na.rm = TRUE),
          "Post-secondary/technical education:", sum(study1$educ_level == 4, na.rm = TRUE),
          "College education or more:", sum(study1$educ_level == 5, na.rm = TRUE)
          )
  ),
  
  min = round(c(
    min(study1$exposure, na.rm = TRUE),
    min(study1$sharing, na.rm = TRUE),
    min(study1$alg_aware, na.rm = TRUE),
    min(study1$wsp, na.rm = TRUE),
    min(study1$ig, na.rm = TRUE),
    min(study1$fb, na.rm = TRUE),
    min(study1$yt, na.rm = TRUE),
    min(study1$tw, na.rm = TRUE),
    min(study1$tiktok, na.rm = TRUE),
    min(study1$age, na.rm = TRUE),
    min(study1$gender, na.rm = TRUE),
    min(study1$rm, na.rm = TRUE),
    min(study1$educ_level, na.rm = TRUE)
  ), 2),
    
  max = round(c(
    max(study1$exposure, na.rm = TRUE),
    max(study1$sharing, na.rm = TRUE),
    max(study1$alg_aware, na.rm = TRUE),
    max(study1$wsp, na.rm = TRUE),
    max(study1$ig, na.rm = TRUE),
    max(study1$fb, na.rm = TRUE),
    max(study1$yt, na.rm = TRUE),
    max(study1$tw, na.rm = TRUE),
    max(study1$tiktok, na.rm = TRUE),
    max(study1$age, na.rm = TRUE),
    max(study1$gender, na.rm = TRUE),
    max(study1$rm, na.rm = TRUE),
    max(study1$educ_level, na.rm = TRUE)
  ), 2),
  
  cronbach = c("", "",
               round(psych::alpha(study1[, c("content_filt", "human_int", "ethic")])$total$raw_alpha, 2),
               "", "", "", "", "", "", "", "", "", ""),
  
  missing = c(
    paste0(round(sum(is.na(study1$exposure)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$sharing)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$alg_aware)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$wsp)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$ig)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$fb)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$yt)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$tw)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$tiktok)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$age)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$gender)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$rm)) / nrow(study1) * 100, 2), "%"),
    paste0(round(sum(is.na(study1$educ_level)) / nrow(study1) * 100, 2), "%")
  )
) |>
  kable(
    col.names = c("Variable", "Mean (SD)/Prop.", "Min.", "Max.", "Cronbach's Alpha", "Missings (%)")
  )

```

# Table A3. Summary Study 2 Variables.
```{r}

data.frame(
  variable = c(
    "Perceived misinformation exposure",
    "Perceived misinformation sharing",
    "Objective news knowledge",
    "Subjective news knowledge",
    "Overconfidence knowledge",
    "Algorithmic Awareness",
    "Algorithmic actions/counteractions",
    "Weekly Whatsapp use",
    "Weekly Instagram use",
    "Weekly Facebook use",
    "Weekly Youtube use",
    "Weekly Twitter use",
    "Weekly Tiktok use",
    "Age (continuous)",
    "Gender",
    "Metropolitan region",
    "Educational level"
  ),
  
  descr = c(
    paste0(round(mean(study2$exposure, na.rm = TRUE), 2), " (", round(sd(study2$exposure, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$sharing, na.rm = TRUE), 2), " (", round(sd(study2$sharing, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$alg_aware, na.rm = TRUE), 2), " (", round(sd(study2$alg_aware, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$counteract_algorithm, na.rm = TRUE), 2), " (", round(sd(study2$counteract_algorithm, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$obj_know, na.rm = TRUE), 2), " (", round(sd(study2$exposure, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$subj_know, na.rm = TRUE), 2), " (", round(sd(study2$exposure, na.rm = TRUE), 2), ")"),
    paste0(round(mean(study2$subj_know_def, na.rm = TRUE), 2), " (", round(sd(study2$exposure, na.rm = TRUE), 2), ")"),
    paste("1:", sum(study2$wsp == 1, na.rm = TRUE), "0:", sum(study2$wsp == 0, na.rm = TRUE)),
    paste("1:", sum(study2$ig == 1, na.rm = TRUE), "0:", sum(study2$ig == 0, na.rm = TRUE)),
    paste("1:", sum(study2$fb == 1, na.rm = TRUE), "0:", sum(study2$fb == 0, na.rm = TRUE)),
    paste("1:", sum(study2$yt == 1, na.rm = TRUE), "0:", sum(study2$yt == 0, na.rm = TRUE)),
    paste("1:", sum(study2$tw == 1, na.rm = TRUE), "0:", sum(study2$tw == 0, na.rm = TRUE)),
    paste("1:", sum(study2$tiktok == 1, na.rm = TRUE), "0:", sum(study2$tiktok == 0, na.rm = TRUE)),
    paste0(round(mean(study2$age, na.rm = TRUE), 2), " (", round(sd(study2$age, na.rm = TRUE), 2), ")"),
    paste("Female:", sum(study2$gender == 0), "Male:", sum(study2$gender == 1)),
    paste("Rm:", sum(study2$rm == 1), "Other:", sum(study2$rm == 0)),
    paste("Primary education or less:", sum(study2$educ_level == 1, na.rm = TRUE),
          "Incomplete secondary education:", sum(study2$educ_level == 2, na.rm = TRUE),
          "Complete secondary education:", sum(study2$educ_level == 3, na.rm = TRUE),
          "Post-secondary/technical education:", sum(study2$educ_level == 4, na.rm = TRUE),
          "College education or more:", sum(study2$educ_level == 5, na.rm = TRUE)
          )
  ),
  
  min = round(c(
    min(study2$exposure, na.rm = TRUE),
    min(study2$sharing, na.rm = TRUE),
    min(study2$obj_know, na.rm = TRUE),
    min(study2$subj_know, na.rm = TRUE),
    min(study2$subj_know_def, na.rm = TRUE),
    min(study2$alg_aware, na.rm = TRUE),
    min(study2$counteract_algorithm, na.rm = TRUE),
    min(study2$wsp, na.rm = TRUE),
    min(study2$ig, na.rm = TRUE),
    min(study2$fb, na.rm = TRUE),
    min(study2$yt, na.rm = TRUE),
    min(study2$tw, na.rm = TRUE),
    min(study2$tiktok, na.rm = TRUE),
    min(study2$age, na.rm = TRUE),
    min(study2$gender, na.rm = TRUE),
    min(study2$rm, na.rm = TRUE),
    min(study2$educ_level, na.rm = TRUE)
  ), 2),
    
  max = round(c(
    max(study2$exposure, na.rm = TRUE),
    max(study2$sharing, na.rm = TRUE),
    max(study2$obj_know, na.rm = TRUE),
    max(study2$subj_know, na.rm = TRUE),
    max(study2$subj_know_def, na.rm = TRUE),
    max(study2$alg_aware, na.rm = TRUE),
    max(study2$counteract_algorithm, na.rm = TRUE),
    max(study2$wsp, na.rm = TRUE),
    max(study2$ig, na.rm = TRUE),
    max(study2$fb, na.rm = TRUE),
    max(study2$yt, na.rm = TRUE),
    max(study2$tw, na.rm = TRUE),
    max(study2$tiktok, na.rm = TRUE),
    max(study2$age, na.rm = TRUE),
    max(study2$gender, na.rm = TRUE),
    max(study2$rm, na.rm = TRUE),
    max(study2$educ_level, na.rm = TRUE)
  ), 2),
  
  cronbach = c("", "", "", 
               round(psych::alpha(study2[, c("p40", "p42", "p44", "p46", "p48", "p50")])$total$raw_alpha, 2),
               round(psych::alpha(study2[, c("content_filt", "human_int", "ethic")])$total$raw_alpha, 2),
               "", "", "", "", "", "", "", "", "", "", "", ""),
  
  missing = c(
    paste0(round(sum(is.na(study2$exposure)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$sharing)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$obj_know)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$subj_know)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$subj_know_def)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$alg_aware)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$counteract_algorithm)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$wsp)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$ig)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$fb)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$yt)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$tw)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$tiktok)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$age)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$gender)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$rm)) / nrow(study2) * 100, 2), "%"),
    paste0(round(sum(is.na(study2$educ_level)) / nrow(study2) * 100, 2), "%")
  )
) |>
  kable(
    col.names = c("Variable", "Mean (SD)/Prop.", "Min.", "Max.", "Cronbach's Alpha", "Missings (%)")
  )

```

# Table A2. Rural and Urban Algorithmic Literacy differences in Study 1.

```{r}
library(dplyr)
library(tidyr)
library(janitor)

# =========================
# 1. Preparar variable zona
# =========================
study1_demo <- study1 %>%
  mutate(
    zona = case_when(
      tipo_zona == 1 ~ "Urban",
      tipo_zona == 2 ~ "Rural",
      TRUE ~ NA_character_
    )
  )%>%
  filter(!is.na(zona))

# =========================
# 2. Tamaño muestral
# =========================
n_zona <- study1_demo %>%
  count(zona, name = "N")

# =========================
# 3. Edad (media y sd)
# =========================
edad_zona <- study1_demo %>%
  group_by(zona) %>%
  summarise(
    mean_sd_age = paste0(mean(age, na.rm = TRUE)%>%round(0)," (", sd(age, na.rm = TRUE)%>%round(0), ")"),
    .groups = "drop"
  )

# =========================
# 4. Nivel educacional
# =========================
educ_zona <- study1_demo %>%
  count(zona, educ_level) %>%
  group_by(zona) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  ungroup()

# =========================
# 5. Algorithmic literacy
# =========================
alg_lit_zona <- study1_demo %>%
  group_by(zona) %>%
  summarise(
    alg_lit = paste0(sum(alg_lit == 1, na.rm = TRUE)," (",round(100 * mean(alg_lit, na.rm = TRUE), 1), ")"),
    .groups = "drop"
  )

# =========================
# 6. Diferencia de medias
# =========================
alg_aware_diff <- with(
  study1_demo,
  t.test(alg_aware ~ zona)
)

diff_table <- tibble(
  diff_means = alg_aware_diff$estimate[1] - alg_aware_diff$estimate[2],
  p_value    = alg_aware_diff$p.value
)

alg_aware_table <- data.frame(
  zona = c("Rural", "Urban"),
  alg_aware_mean = c("2.2 (p > 0.01)", "2.8")
)

# =========================
# 7. Gender by zone
# =========================
gender_zona <- study1_demo %>%
  mutate(
    gender_lab = case_when(
      gender == 1 ~ "Women",
      gender == 0 ~ "Men",
      TRUE ~ NA_character_
    )
  ) %>%
  count(zona, gender_lab) %>%
  group_by(zona) %>%
  mutate(
    gender_pct = round(100 * n / sum(n), 1),
    gender_freq_pct = paste0(n, " (", gender_pct, "%)")
  ) %>%
  ungroup() %>%
  select(zona, gender_lab, gender_freq_pct) %>%
  pivot_wider(
    names_from = gender_lab,
    values_from = gender_freq_pct
  )

gender_tabla <- data.frame(
  zona = c("Rural", "Urban"),
  gender = c("M: 184 (41%) / W: 265 (59%)", "M: 327 (43.5%) / W: 424 (56.5%)")
)

# =========================
# 8. Educational level by zone
# =========================
educ_zona <- study1_demo %>%
  mutate(
    educ_lab = case_when(
      educ_level == 1 ~ "Basic education",
      educ_level == 2 ~ "Middle school (incomplete)",
      educ_level == 3 ~ "Middle school (complete)",
      educ_level == 4 ~ "Technical higher education",
      educ_level == 5 ~ "University / Postgraduate",
      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(educ_lab)) %>%
  count(zona, educ_lab) %>%
  group_by(zona) %>%
  mutate(
    educ_pct = round(100 * n / sum(n), 1),
    educ_item = paste0(educ_lab, ": ", n, " (", educ_pct, "%)")
  ) %>%
  summarise(
    Education = paste(educ_item, collapse = "; "),
    .groups = "drop"
  )



# =========================
# 9. Tabla resumen principal
# =========================
tabla_principal <- n_zona %>%
  left_join(alg_lit_zona, by = "zona") %>%
  left_join(alg_aware_table, by = "zona") %>%  
  left_join(edad_zona, by = "zona") %>%
  left_join(gender_tabla, by = "zona") %>%
  left_join(educ_zona, by = "zona") %>%
  rename(
    "Area" = zona,
    "Know Algorithmic Term" = alg_lit,
    "Algorithmic Awareness mean" = alg_aware_mean,
    "Age Mean (sd)" = mean_sd_age,
    "Gender" = gender
  )


tabla_principal %>%
  kable()
#openxlsx::write.xlsx(tabla_principal, "data/rural_comparation_study1.xlsx")

  
```



# Modelos

```{r}
study1 <- study1 %>%
  mutate(
    sharing_original = ifelse(is.na(sharing_original), NA, sharing_original)
    )

study2 <- study2 %>%
  mutate(
    sharing_original = ifelse(is.na(sharing_original), NA, sharing_original)
    )

study1_model <- study1|>
  mutate_at(.vars = vars(gender,rm, sharing_categorical),
            .funs = list(~to_label(.)))|>
  mutate_at(.vars = vars(ppal_ocupation,educ_level),
            .funs = list(~to_numeric(.)))

study2_model <- study2|>
  mutate_at(.vars = vars(gender,rm,sharing_categorical),
            .funs = list(~to_label(.)))|>
  mutate_at(.vars = vars(ppal_ocupation,educ_level),
            .funs = list(~to_numeric(.)))
```

```{r}
exposure_a <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study1_model)

exposure_b <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study2_model)


sjPlot::tab_model(list(exposure_a,exposure_b), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Study 1","Study 2"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Region (MR = 1)", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  string.pred = "Predictors", 
                  string.est = "β",
                  show.se = T,
                  title = "Table 1. OLS model Perceived misinformation exposure")
```

```{r}
sharing_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")

sharing_b <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study2_model,family = "binomial")

sjPlot::tab_model(list(sharing_a,sharing_b), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Study 1","Study 2"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Metropolitan Region", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  string.pred = "Predictors", 
                  string.est = "β (Logit)",
                  show.se = T,
                  title = "Table 2. Logistic model Perceived misinformation sharing",
                  transform = NULL)
```

# Table 2. OLS Models for Study 2
```{r}
exposure_3b <- lm(exposure ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                data=study2_model)

obj_know_model<-lm(obj_know ~ alg_aware+counteract_algorithm+
                     age+gender+rm+educ_level+
                     wsp+ig+fb+yt+tw+tiktok,
                   data=study2_model)

subj_know_model <- lm(subj_know ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                      wsp+ig+fb+yt+tw+tiktok,
                  data=study2_model)

score_model <- lm(subj_know_def ~ alg_aware+counteract_algorithm+
                        age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                      data=study2_model)

sjPlot::tab_model(exposure_3b,obj_know_model,subj_know_model,score_model,
          show.ci = FALSE,
          p.style = "stars",
          dv.labels = c("Perceived Misinformation Exposure",
                        "Objective news knowledge",
                        "Subjective news knowledge",
                        "Knowledge overconfidence"),
          pred.labels = c("(Intercept)",
                          "Alg. Awareness",
                          "Alg. counteractions",
                          "Age",
                          "Gender (Women = 1)",
                          "Metropolitan Region", 
                          "Educational level",
                          "Whatsapp weekly use", 
                          "Instagram weekly use", 
                          "Facebook weekly use", 
                          "Youtube weekly use", 
                          "Twitter weekly use", 
                          "TikTok weekly use"),
          show.se = T,
          string.est = "β",
          title = "Table 3. OLS models Study 2")
```


# Plot Models

```{r}
library(dplyr)
library(haven)

exposure_a <- lm(exposure ~ 
                   alg_aware + age + gender + rm + educ_level +
                   wsp + ig + fb + yt + tw + tiktok,
                 data = study1_model)

exposure_b <- lm(exposure ~ 
                   alg_aware + age + gender + rm + educ_level +
                   wsp + ig + fb + yt + tw + tiktok,
                 data = study2_model)

plot_models(exposure_a, exposure_b,
            show.values = TRUE,
            show.p = TRUE,
            ci.lvl = 0.95,
            m.labels = c("Study 1", "Study 2"),
            axis.labels = rev(c("Alg. Awareness", "Age", "Gender (female)",
                                "Region (Metropolitana)", "Educational level",
                                "Whatsapp weekly use", "Instagram weekly use",
                                "Facebook weekly use", "Youtube weekly use",
                                "Twitter weekly use", "TikTok weekly use")),
            title = "Figure 1. Predictors of perceived misinformation exposure") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom")



```
```{r}
plot_model(sharing_a, 
           transform = NULL,   # 👈 esto evita que se expongan y los deja en logit
           show.values = TRUE, 
           value.offset = .3,
           title = "Predicting misinformation sharing (logit coefficients)",
           axis.labels = rev(c("Algorithmic awareness",
                               "Age",
                               "Gender (female)",
                               "Region (Metropolitan)",
                               "Educational level",
                               "WhatsApp weekly use",
                               "Instagram weekly use",
                               "Facebook weekly use",
                               "YouTube weekly use",
                               "X (Twitter) weekly use",
                               "TikTok weekly use"))) 

```

```{r}
# Plot para los cuatro modelos de Study 2
plot_models(exposure_3b, obj_know_model, subj_know_model, score_model,
            show.values = TRUE,
            show.p = TRUE,
            ci.lvl = 0.95,
            m.labels = c("Exposure", "Objective knowledge", 
                         "Subjective knowledge", "Overconfidence"),
            axis.labels = rev(c("Alg. Awareness", "Alg. counteractions",
                                "Age", "Gender (female)",
                                "Region (Metropolitana)", "Educational level",
                                "Whatsapp weekly use", "Instagram weekly use",
                                "Facebook weekly use", "Youtube weekly use",
                                "Twitter weekly use", "TikTok weekly use")),
            title = "Figure 3. Predictors of exposure and knowledge (Study 2)") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom")
```

# Appendix

# Table A4. Comparative models study 1 (Filter Alg. Lit.)

```{r}
s1_filter1 <- study1|>
  filter(alg_lit_test == 1)|>
  mutate(
    gender = to_label(gender),
    rm = to_label(rm)
  )

s1_filter2 <- study1|>
  filter(alg_lit_test == 0)|>
  mutate(
    gender = to_label(gender),
    rm = to_label(rm)
  )

exposure_a <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study1_model)

exposure_filter_a <- lm(exposure ~ 
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = s1_filter1)

exposure_interaction_a <- lm(exposure ~ 
                   alg_aware*alg_lit_test + 
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,
                  data = study1_model)

sharing_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")

sharing_filter_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                
                   data = s1_filter1,family = "binomial")

sharing_interaction_a <- glm(sharing~
                   alg_aware*alg_lit_test + 
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")

# lm.beta(exposure_a)
#lm.beta(exposure_filter_a)

#effectsize::standardize_parameters(sharing_a)
#effectsize::standardize_parameters(sharing_filter_a)


sjPlot::tab_model(list(exposure_a, exposure_filter_a,
                       sharing_a, sharing_filter_a), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Exposure: Original","Exposure: Alg == 1",
                                "Sharing: Original", "Sharing: Alg == 1"),
                  string.est = c("β (OLS/Logit)"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Region (MR = 1)", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  title = "Table X. Comparative models study 1 (Filter Alg. Lit.)",
                  transform = NULL)


```

```{r}
```


## Sharing with original scale

```{r}

sharing_a_original <- lm(sharing_original~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model)

sharing_a <- glm(sharing~
                   alg_aware+
                   age+gender+rm+educ_level+
                   wsp+ig+fb+yt+tw+tiktok,                  
                   data = study1_model,family = "binomial")


sjPlot::tab_model(list(sharing_a, sharing_a_original), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Sharing Dicothomical Study 1","Sharing Study 1 Continue Scale"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Region (MR = 1)", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  title = "Table X. Comparative models Sharing recodification Study 1",
                  transform = NULL)
```

# Table 3. Multinomial model for Sharing Misinformation in Study 2

```{r}
library(nnet)

# Study 2: Binomial model (already specified, included here for completeness)
#sharing_b <- glm(
 # sharing ~
  #  alg_aware + counteract_algorithm +
   # age + gender + rm + educ_level +
    #wsp + ig + fb + yt + tw + tiktok,
  #data = study2_model,
  #family = "binomial"
#)

# Study 2: Multinomial model
sharing_b_original <- multinom(
  sharing_categorical ~
    alg_aware + counteract_algorithm +
    age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2_model,
  trace = FALSE
)

# Comparative table
sjPlot::tab_model(
  list(
#    sharing_b,
    sharing_b_original
  ),
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = c(
 #   "Sharing Dichotomical Study 2",
    "Sharing Study 2 Categorical (Multinomial)"
  ),
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Alg. Awareness",
    "Age",
    "Age",
    "Gender (Women = 1)",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Educational level",
    "Whatsapp weekly use",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "Twitter weekly use",
    "TikTok weekly use",
    "TikTok weekly use"
  ),
  title = "Table X. Sharing study 2"
)
```

# Objective Knowledge recodification

```{r}
library(nnet)
library(sjPlot)

# -----------------------------
# Logistic models (Correct vs Not correct)
# -----------------------------

know_p39_logit <- glm(
  p39_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

know_p41_logit <- glm(
  p41_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

know_p43_logit <- glm(
  p43_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

know_p45_logit <- glm(
  p45_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

know_p47_logit <- glm(
  p47_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

know_p49_logit <- glm(
  p49_a ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, family = "binomial"
)

# -----------------------------
# Multinomial models (Correct / Incorrect / Don't know)
# -----------------------------

know_p39_multi <- multinom(
  p39_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)

know_p41_multi <- multinom(
  p41_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)

know_p43_multi <- multinom(
  p43_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)

know_p45_multi <- multinom(
  p45_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)

know_p47_multi <- multinom(
  p47_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)

know_p49_multi <- multinom(
  p49_b ~ alg_aware + age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2, trace = FALSE
)
```

```{r}
sjPlot::tab_model(
  list(
    know_p39_logit,
    know_p41_logit,
    know_p43_logit,
    know_p45_logit,
    know_p47_logit,
    know_p49_logit
  ),
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = c(
    "P39 Correct vs Not",
    "P41 Correct vs Not",
    "P43 Correct vs Not",
    "P45 Correct vs Not",
    "P47 Correct vs Not",
    "P49 Correct vs Not"
  ),
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table X.a. Logistic models predicting correct objective knowledge (Study 2)"
)

```

```{r}
sjPlot::tab_model(
  know_p39_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P39 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A1. Multinomial model for P39 (Correct / Incorrect / Don't know)"
)

sjPlot::tab_model(
  know_p41_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P41 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A2. Multinomial model for P41 (Correct / Incorrect / Don't know)"
)

sjPlot::tab_model(
  know_p43_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P43 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A3. Multinomial model for P43 (Correct / Incorrect / Don't know)"
)

sjPlot::tab_model(
  know_p45_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P45 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A4. Multinomial model for P45 (Correct / Incorrect / Don't know)"
)

sjPlot::tab_model(
  know_p47_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P47 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A5. Multinomial model for P47 (Correct / Incorrect / Don't know)"
)

sjPlot::tab_model(
  know_p49_multi,
  show.ci = FALSE,
  show.se = TRUE,
  p.style = "stars",
  dv.labels = "P49 Objective knowledge",
  pred.labels = c(
    "(Intercept)",
    "Alg. Awareness",
    "Age",
    "Gender (Women = 1)",
    "Region (MR = 1)",
    "Educational level",
    "Whatsapp weekly use",
    "Instagram weekly use",
    "Facebook weekly use",
    "Youtube weekly use",
    "Twitter weekly use",
    "TikTok weekly use"
  ),
  title = "Table A6. Multinomial model for P49 (Correct / Incorrect / Don't know)"
)

```

# Table study 1

```{r}
sjPlot::tab_model(list(exposure_a,sharing_a_original), 
                  show.ci=FALSE, 
                  p.style = "stars", 
                  dv.labels = c("Exposure","Sharing"),
                  pred.labels = c("(Intercept)",
                                  "Alg. Awareness",
                                  "Age",
                                  "Gender (Women = 1)",
                                  "Region (MR = 1)", 
                                  "Educational level",
                                  "Whatsapp weekly use", 
                                  "Instagram weekly use", 
                                  "Facebook weekly use", 
                                  "Youtube weekly use", 
                                  "Twitter weekly use", 
                                  "TikTok weekly use"),
                  string.pred = "Predictors", 
                  string.est = "β",
                  show.se = T,
                  transform = NULL,
                  title = "Table 1. Predicting Missinformation Exposure and Sharing in Study 1")
```

# Table Study 2

```{r}
exposure_3b <- lm(exposure ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                data=study2_model)

obj_know_model<-lm(obj_know ~ alg_aware+counteract_algorithm+
                     age+gender+rm+educ_level+
                     wsp+ig+fb+yt+tw+tiktok,
                   data=study2_model)

subj_know_model <- lm(subj_know ~ alg_aware+counteract_algorithm+
                    age+gender+rm+educ_level+
                      wsp+ig+fb+yt+tw+tiktok,
                  data=study2_model)

score_model <- lm(subj_know_def ~ alg_aware+counteract_algorithm+
                        age+gender+rm+educ_level+
                    wsp+ig+fb+yt+tw+tiktok,
                      data=study2_model)

sjPlot::tab_model(exposure_3b,obj_know_model,subj_know_model,score_model,
          show.ci = FALSE,
          p.style = "stars",
          dv.labels = c("Perceived Misinformation Exposure",
                        "Objective news knowledge",
                        "Subjective news knowledge",
                        "Knowledge overconfidence"),
          pred.labels = c("(Intercept)",
                          "Alg. Awareness",
                          "Alg. counteractions",
                          "Age",
                          "Gender (Women = 1)",
                          "Metropolitan Region", 
                          "Educational level",
                          "Whatsapp weekly use", 
                          "Instagram weekly use", 
                          "Facebook weekly use", 
                          "Youtube weekly use", 
                          "Twitter weekly use", 
                          "TikTok weekly use"),
          string.est = "β",
          show.se=T, 
          title = "Table 3. OLS models Study 2")
```

# Table Sharing study 2

```{r}
library(nnet)
# Study 2: Multinomial model
sharing_b_original <- multinom(
  sharing_categorical ~
    alg_aware + counteract_algorithm + subj_know_def +
    age + gender + rm + educ_level +
    wsp + ig + fb + yt + tw + tiktok,
  data = study2_model,
  trace = FALSE
)

sjPlot::tab_model(sharing_b_original,
          show.ci = FALSE,
          p.style = "stars",
          dv.labels = c("Sharing Missinformation"),
          string.est = "β (Logit)",
          pred.labels = c("(Intercept)",
                          "Alg. Awareness",
                          "Alg. counteractions",
                          "Knowledge Miscalibration",
                          "Age",
                          "Gender (Women = 1)",
                          "Metropolitan Region", 
                          "Educational level",
                          "Whatsapp weekly use", 
                          "Instagram weekly use", 
                          "Facebook weekly use", 
                          "Youtube weekly use", 
                          "Twitter weekly use", 
                          "TikTok weekly use",
                          "(Intercept)",
                          "Alg. Awareness",
                          "Alg. counteractions",
                          "Knowledge Miscalibration",
                          "Age",
                          "Gender (Women = 1)",
                          "Metropolitan Region", 
                          "Educational level",
                          "Whatsapp weekly use", 
                          "Instagram weekly use", 
                          "Facebook weekly use", 
                          "Youtube weekly use", 
                          "Twitter weekly use", 
                          "TikTok weekly use"),
          show.se=T, 
          transform = NULL,
          title = "Table 3. Multinomial model Sharing Study 2")
```

# Calcular F test

```{r}
# Study 1: Global F-tests

#summary(exposure_a)
#summary(sharing_a_original)

# Alternativamente (misma información del test global)
#anova(exposure_a)
#anova(sharing_a_original)

```

```{r}
# Study 2: Global F-tests for OLS models

#summary(exposure_3b)
#summary(obj_know_model)
#summary(subj_know_model)
#summary(score_model)

# O bien
#anova(exposure_3b)
#anova(obj_know_model)
#anova(subj_know_model)
#anova(score_model)

```
```{r}
#sharing_null <- multinom(
#  sharing_categorical ~ 1,
 # data = study2_model,
  #trace = FALSE
#)

#anova(sharing_null, sharing_b_original, test = "Chisq")


```

